Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
turn Supplementals into a (temporary) mess

\subsection{Congruencies across contrasts}

@@

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and
overall eight $t$-contrast for the audio-description stimulus (Tab.~\ref{tab:av-contrasts})
by varying the contrasted categories (and thus the
amount of available data), and how well the annotated events within categories
on average matched a stimulus type that we assumed to correlate with spatial
perception.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
All five movie contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (Fig.~\ref{fig:stability-slices}).
% AV: RSC & LOC
Reliably across contrasts of the movie stimulus, we find bilaterally
significant clusters also in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
occipital cortex (contrasts 1, 2, 4, 5).

@@

% AD: results
For the audio-description stimulus, all contrasts except contrast 7
(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
clusters in anterior regions of the group PPA overlap (Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Reliably across contrast of the audio-description stimulus, we find bilaterally significant
clusters also in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).
% non-systematic
Lastly, some contrasts of the audio-description stimulus yielded significant clusters in
regions that were not statistically significant in three or more contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum, left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.

@@

% Discussion
The results across the contrasts of the movie and audio-description stimulus indicate that our
findings regarding the PPA but also RSC and LOC are robust and do not depend on
the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

>>>>

\subsection{Additional contrasts: PPA, RSC, and LOC (AV \& AV)}

@@

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and overall
eight $t$-contrast for the audio-description stimulus
(Tab.~\ref{tab:av-contrasts}).
% how
Contrasts differ in contrasted categeories based on ``how well'' averaged
events within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
All five movie contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (Fig.~\ref{fig:stability-slices}).
% AV: RSC & LOC
Also reliably across contrasts of the movie stimulus, we find bilaterally
significant clusters in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
occipital cortex (contrasts 1, 2, 4, 5).

@@

% AD: results
For the audio-description stimulus, all contrasts except contrast 7
(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
clusters in anterior regions of the group PPA overlap
(Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
We find bilaterally significant clusters also in the ventral precuneus (all
except contrasts 8), lateral occipital cortex (bilateral in contrasts 1 to 4;
unilateral in contrasts 6 and 7).
% "Discussion" of PPA, RSC, and LOC
The results across the contrasts of the movie and audio-description stimulus
indicate that our findings regarding the PPA but also RSC and LOC are robust and
do not depend on the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

\subsection{Additional contrasts: let's talk about left overs}

\todo[inline]{look at the events within categories \& give some counts}

\todo[inline]{compare with Michaels make over of text regarding confound
structure

\todo[inline]{main message here again: you need events! (and be aware of biases)}

%
Three contrasts yielded bilaterally significant clusters in superior temporal
cortices (contrasts 3, 6, 7), one contrast a unilateral right cluster (contrast
2).
%
\todo{following is (probably too) exhaustive}
%
Lastly, some contrasts of the audio-description stimulus yielded significant
clusters in regions that were not statistically significant in three or more
contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% concludion statement
Conclusion: This can be attributed to the uncontrolled nature of averaged events.
